\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-04-15 archive.tex
improvement to waking sleeping figure but still in progress

    \begin{scope}[shift={(0.5,0.5)}]
      \node[align=right] at (0,-0.5) (d){\textbf{Library}\\
        $f_1$, $f_2$, ...};
      \node[align=center] at ([yshift = -2cm]d) (t){\textbf{Task}\\
        \footnotesize            \code{[7\, 2\, 3]}$\to$\code{[7\, 3]}         \\
        \footnotesize    \code{[4\, 3\, 2\, 1]}$\to$\code{[4\, 3]} };

@@

      \node[align=left] at ([xshift=3cm]s.east) (f) {\textbf{Programs:}\\
        \small    \code{($f_1$ $\ell$ ($\lambda$ (x) (> x 2)))}\\
        \small $\cdots\cdots\cdots$};
      \draw [->  ] (s.east) -- (f.west);

@@

    \node at (0,-4.75) {\textbf{\textsc{Sleep: Consolidation}}};
    \draw[fill=teal!5!white] (-3,-5) -- (3,-5) -- (3,-10) -- (5.5,-10) -- (5.5,-13) -- (-3,-13) -- (-3,-5);
    \node at (12,-4.75) {\textbf{\textsc{Sleep: Dreaming}}};
    \draw[fill=teal!5!white] (15,-5) -- (9,-5) -- (9,-10) -- (6.5,-10) -- (6.5,-13) -- (15,-13) -- (15,-5);

@@

  \end{tikzpicture}
  \caption{\textbf{Middle:} \system as a graphical model. Agent observes programming tasks (e.g., input/outputs for list processing or images for graphics programs), which it explains with latent programs, while jointly inferring a latent library capturing cross-program regularities. A neural network, called the \emph{recognition model} (red arrows) is trained to quickly infer programs with high posterior probability. \textbf{Top}: Wake phase infers programs while holding the library and recognition model fixed. \textbf{Left}: Sleep (Consolidation) phase updates library while holding the programs fixed by refactoring programs found during waking and extracting common components. \textbf{Right}: Sleep (Dreaming) phase trains recognition model to predict approximate posterior over programs conditioned on task. Trained on `Fantasies' (programs sampled from library) \& `Replays' (programs found during waking).}\label{threeCycles}
\end{figure}

>>>>

    \begin{scope}[shift={(0.5,0.5)}]
      \node[align=center] at (0,-0.5) (d){\textbf{Library}\\
        \code{$f_1($x$)=$(+ x 1)}\\
        \code{$f_2($z$)=$(fold cons (cons z nil))}\\
         ...};
      \node[align=center] at ([yshift = -2cm]d) (t){\textbf{Task}\\
        \footnotesize            \code{[7\, 2\, 3]}$\to$\code{[4 3 8]}         \\
        \footnotesize    \code{[3\, 8]}$\to$\code{[9 4]}\\
        \footnotesize    \code{[4\, 3\, 2]}$\to$\code{[3 4 5]} };

@@

      \node[align=left] at ([xshift=3cm]s.east) (f) {\textbf{Programs:}\\
        \small    \code{(map $f_1$ (fold $f_2$ nil x))}\\
        \small $\cdots\cdots\cdots$};
      \draw [->  ] (s.east) -- (f.west);

@@

    \node at (0,-4.75) {\textbf{\textsc{Sleep: Abstraction}}};
    \draw[fill=teal!5!white] (-3,-5) -- (3,-5) -- (3,-10) -- (5.5,-10) -- (5.5,-13) -- (-3,-13) -- (-3,-5);
    \node at (12,-4.75) {\textbf{\textsc{Sleep: Dreaming}}};
    \draw[fill=teal!5!white] (15,-5) -- (9,-5) -- (9,-10) -- (6.5,-10) -- (6.5,-13) -- (15,-13) -- (15,-5);

@@

  \end{tikzpicture}
  \caption{\textbf{Middle:} \system as a graphical model. Agent observes programming tasks (e.g., input/outputs for list processing or images for graphics programs), which it explains with latent programs, while jointly inferring a latent library capturing cross-program regularities. A neural network, called the \emph{recognition model} (red arrows) is trained to quickly infer programs with high posterior probability. \textbf{Top}: Wake phase infers programs while holding the library and recognition model fixed. \textbf{Left}: Sleep (Abstraction) phase updates library while holding the programs fixed by refactoring programs found during waking and abstracting out common components (highlighted in orange). \textbf{Right}: Sleep (Dreaming) phase trains recognition model to predict approximate posterior over programs conditioned on task. Trained on `Fantasies' (programs sampled from library) \& `Replays' (programs found during waking).}\label{threeCycles}
\end{figure}
